%!TEX root = ../report.tex
\documentclass[../report.tex]{subfiles}

\begin{document}
    \section{Conclusions}
    \label{sec:conclusions}
    Developing and evaluating our framework for radioactive source localization has provided valuable insights into the relative performance of different 
    localization strategies. This method combines physics-based radiation simulation with systematic evaluation methods to compare three distinct approaches: information-gain-based
    and inverse square law optimization algorithms. Our experiments and evaluation across multiple source configurations demonstrate that each method can localize sources with
    varying efficiency and accuracy. The information-gain-based algorithm is a winner regarding convergence time and achieving the lowest
    position error in source localization. The rollout algorithm also performs well but with a slightly higher convergence time and consistently predicts a position error of around 7 meters due to the selection of a grid resolution of 5 meters. While effective, the inverse square law optimization algorithm 
    takes significantly longer to converge and, with some source configurations, position in this case, witnesses a higher error. It is also worth noting that the evaluation metrics are the convergence time and the position error. The convergence time also includes the movement time, and a 
    drone with better movement control might achieve better performance in the time taken.

    \subsection{Summary}
    \label{sec:conclusions:summary}

    Our comprehensive evaluation of three distinct approaches to radiation source localization - information-gain-based, rollout-based, and inverse square law 
    optimization - revealed several significant findings. Statistical analysis demonstrated that while all three methods achieved comparable accuracy in source 
    localization, with errors ranging from 4.5 to 14.4 meters, they exhibited marked differences in convergence speed. The information-gain-based approach 
    consistently demonstrated superior performance, achieving convergence in 43-126 seconds, followed by the rollout algorithm at 90-177 seconds. Both methods 
    significantly outperformed the baseline inverse square method, which required 415-470 seconds for convergence.

    The Wilcoxon Signed-Rank Test demonstrated significant differences in convergence times among the algorithms, with large effect sizes (r = 0.8864) supporting 
    this finding. This statistical evidence and practical performance metrics strongly validate the effectiveness of information-theoretic methods in radiation 
    source localization.

    \subsection{Contributions}
    \label{sec:conclusions:contributions}

    This research makes several contributions to the field of autonomous radiation source localization. First, we have developed a physics-based 
    simulation framework that incorporates realistic radiation behavior, including particle attenuation and scattering effects. This framework provides a reliable
    platform for testing and evaluating localization algorithms under controlled conditions.

    Second, our implementation and comparative analysis of three distinct localization approaches establishes quantitative benchmarks for algorithm performance. 
    The systematic evaluation methodology we developed, combining both practical performance metrics and rigorous statistical analysis, provides a framework 
    for assessing future algorithms in this domain.

    Third, our results demonstrated that, in the domain of radioactive source localization, the information-based methods could perform significantly better than
    the traditional predefined trajectory following methods without compromising accuracy and time. This study offers a promising direction for developing 
    autonomous methods that may need to find radioactive sources


    \subsection{Future Work}
    \label{sec:conclusions:future_work}
\end{document}
